% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 10pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen,  enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=0.8in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}


% --- Document starts here ---

\begin{document}
% Name and date of last update to this document
\noindent{\huge{Erica Lindsey Busch}
\hfill{\it\small Updated June 26, 2025}}

% --- Contact information and other items ---

\begin{table}[h]%{p{1in}p{5.5in}}
\textbf{Email:} \href{erica.busch@yale.edu}{erica.busch@yale.edu}\hfill
\textbf{Website:} \href{https://ericabusch.github.io/}{ericabusch.github.io}\\
\textbf{Github:} \href{http://www.github.com/ericabusch}{github.com/ericabusch}\hfill 
\textbf{LinkedIn:} \href{http://www.linkedin.com/in/erica-busch}{linkedin.com/in/erica-busch}
\end{table}


% --- Section: Education ---

\section*{Education}
\textbf{Yale University} \hfill August 2020 -- Present\\ 
PhD Candidate, Neuroscience \hfill Department of Psychology\\
Master of Philosophy, Master of Science\hfill 2023\\
Thesis: Understanding and enhancing human cognition along neural manifolds\\
Advisor: Nicholas Turk-Browne\vspace{0.4cm}

\noindent{\textbf{Dartmouth College} \hfill September 2016 -- March 2020}\\
BA in Cognitive Science, Computer Science \hfill High Honors\\
Thesis: A deep learning approach to scene perception in autism\\
Advisors: James Haxby, Caroline Robertson\vspace{0.4cm}

\noindent{\textbf{Centro Tinku Academic Center} \hfill August -- November 2017\\}
Advanced Language Study Abroad in Spanish \hfill Cusco, Peru

% --- Section: Awards, scholarships, etc. ---
\section*{Awards and honors}

\noindent{{ReproNim/INCF Fellowship (\$700)}}\hfill 2024--2026\\
\noindent{\small{\textit{Center for Reproducible Neuroimaging Train-the-Trainer Program}}}\vspace{0.2cm}

\noindent{Conference Travel Fellowship (\$800)} \hfill 2025\\
\noindent{\small{\textit{Yale University Graduate Student Assembly}}}\vspace{0.2cm}

\noindent{{Google PhD Fellowship} (Finalist) \hfill 2024}\vspace{0.2cm}

\noindent{Society for Neuroscience Annual Meeting Travel Award (\$500)}\hfill 2023\\
\noindent{\small{\textit{Wu Tsai Institute at Yale University}}}\vspace{0.2cm}

\noindent{Social and Affective Neuroscience Society Naturalistic Data Challenge (First Prize)} \hfill 2022\\
\noindent{\small{\textit{Project title: }Relating neural dynamics and emotion dynamics with
nonlinear manifold learning}} \vspace{0.2cm}

\noindent{{National Science Foundation Graduate Research Fellowship} (\$138,000)   \hfill 2021--2024}\\
\noindent{\small{\textit{Project title:} {Enhancing human learning along neural manifolds}}}\vspace{0.2cm}

\noindent{{Outstanding Undergraduate Research Award} (2nd Prize)\hfill 2020}\\
\noindent{\small{\textit{Neukom Institute for Computational Science}}}\vspace{0.2cm}

\noindent{``Made at Dartmouth'' Research Competition Winner (First Prize)\hfill 2020}\\
\noindent{\small{\textit{Dartmouth College Undergraduate Advising and Research}, \href{https://www.youtube.com/watch?v=mOtlF0ywH_s&ab_channel=MediaProjDartmouth}{video}}}\vspace{0.2cm}

\noindent{Academic Achievement Prize in Cognitive Science\hfill 2020}\vspace{0.2cm}

\noindent{{Fulbright Fellowship} (Finalist, withdrew due to COVID-19)\hfill 2020}\vspace{0.2cm}

\noindent{High Honors in Cognitive Science\hfill 2020}\vspace{0.2cm}

\noindent{{William H. Neukom Scholarship} (\$1,000, awarded twice) \hfill 2019-2020}\\
\noindent{\small\textit{Neukom Institute for Computational Science}}\vspace{0.2cm}

\noindent{{Citation for Academic Excellence in Machine Learning}\hfill 2019}\\
\noindent{\small\textit{{Dartmouth College Department of Computer Science}}}\vspace{0.2cm}

\noindent{{National Science Foundation Research Experience for Undergraduates} (\$5,500) \hfill 2019}\\
\noindent{\small{\textit{University of Washington Center for Neurotechnology}}}\\
\noindent{\small{\textit{Project title:} {Deep learning models of octopus arm decision-making}}}\vspace{0.2cm}

\noindent{{Citation for Academic Excellence in Cognitive Neuroscience (graduate level)} \hfill 2019}\\
\noindent{\small{\textit{Dartmouth College Department of Psychological and Brain Sciences}}}\vspace{0.2cm}

\noindent{David C. Hodgson Endowment Award for Cognitive Neuroscience Research (\$5,000) \hfill 2019}\\
\noindent{\small{\textit{Dartmouth College Undergraduate Advising and Research}}}\vspace{0.2cm}

\noindent{{James O. Freedman Presidential Scholarship} (\$1,000, awarded twice) \hfill 2018--2019}\\
\noindent{\small{\textit{Dartmouth College Undergraduate Advising and Research}}}\vspace{0.2cm}

\noindent{{Sophomore Research Scholarship}, Dartmouth College (\$1,000) \hfill 2018}\\
\noindent{\small{\textit{Dartmouth College Undergraduate Advising and Research}}}\vspace{0.2cm}

\noindent{{Citation for Academic Excellence} in Introduction to Programming \& Computation\hfill2017}\\
\noindent{\small{\textit{Dartmouth College Department of Computer Science}}}\vspace{0.2cm}

\noindent{{Honors List}, Dartmouth College\hfill2017-2020}\vspace{0.2cm}\\
\noindent{{National Merit Scholarship} (Finalist)\hfill2015}\vspace{0.2cm}

\noindent{\small\textit{** Awarded scholarship,  fellowship, \& grant amounts in USD}}\\

% --- Section: Publications ---
\section*{Publications}
\subsection*{Peer-reviewed articles and conference proceedings}

\noindent{\textbf{Busch, E.L.} \& Turk-Browne, N.B. (2025). Intrinsic dimensionality of brain activity manifolds across tasks and development. \textit{Accepted, Proceedings of the 8th Annual Conference on Cognitive Computational Neuroscience}. \vspace{0.2cm}}

\noindent{Afrasiyabi, A., Bhaskar, D., \textbf{Busch, E.L.,} Caplette, L., Singh, R., Lajoie, G., Turk-Browne, N.B., \& Krishnaswamy, S. (2025). Latent representation learning for multimodal brain activity translation. \textit{IEEE International Conference on Acoustics, Speech, and Signal Processing [ICASSP2025]}. 10.1109/ICASSP49660.2025.10887834}\vspace{0.2cm} 

\noindent{\textbf{Busch, E.L.*,} Conley, M.I.*, \& Baskin-Somers, A. (2024). Manifold learning uncovers nonlinear interactions between the adolescent brain and environment that predict emotional and behavioral problems. \textit{Biological Psychiatry: Cognitive Neuroscience and Neuroimaging}. doi.org/10.1016/j.bpsc.2024.07.001\\ 
\small{ $\bullet$ Analysis repository: github.com/ericabusch/manifold\_abcd\_psychopathology\_bpcnni}\\
\small{$\bullet$ PIP package: pypi.org/project/EPHATE/}}\vspace{0.2cm}

\noindent{Roskies, A., \textbf{Busch, E.L.}, \& Walton, A. Agency as a framework for thinking about neuropsychiatric disease: A prelude to asking causal questions. \textit{Causal Concepts in Psychopathology: Multidisciplinary Perspectives}, Cambridge University Press. \vspace{0.2cm}}

\noindent{\textbf{Busch, E.L.}, Fincke, E.C., Lajoie, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2024). Learning along the manifold of human brain activity via real-time neurofeedback. \textit{Proceedings of the 7th Annual Conference on Cognitive Computational Neuroscience}.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Rapuano, K.M., Anderson, K.M., Rosenberg, M.D., Watts, R., Casey, BJ, Haxby, J.V., \& Feilong, M. (2024). Dissociation of reliability, predictability, and heritability in fine- and coarse-scale functional connectomes during development. \textit{Journal of Neuroscience}. 44(6), doi:10.1523/JNEUROSCI.0735-23.2023.\\
\small{$\bullet$ Analysis repository: github.com/ericabusch/ABCD\_hyperalignment\_JNeurosci}}\vspace{0.2cm}

\noindent{Skalaban, L.J., Chan, I., Lin, Q., Rapuano, K.M., Conley, M.I., \textbf{Busch, E.L.}, Watts, R., Murty, V., \& Casey, B.J. (2024). Representational dissimilarity of faces and places during a working memory task is associated with subsequent recognition memory during development. \textit{Journal of Cognitive Neuroscience}. 36(3) 415-434, doi:10.1162/jocn\_a\_02094.}\vspace{0.2cm} 

\noindent{Afrasiyabi, A., \textbf{Busch, E.L.,} Singh, R., Bhaskar, D., Capette, L., Turk-Browne, N.B., Krishnaswamy, S. (2024). Looking through the mind's eye via multimodal encoder-decoder networks. \textit{Machine as Medium: Proceedings of the Center for Collaborative Arts and Media}, Fall 2024 Volume. doi:10.48550/arXiv.2410.00047.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Yates, T.S., \& Turk-Browne, N.B. (2023). Tasks collapse the intrinsic dimensionality of activity in non-selective cortex. \textit{Proceedings of the 6th Annual Conference on Cognitive Computational Neuroscience}.\vspace{0.2cm}}

\noindent{\textbf{Busch, E.L.}, Huang, J., Benz, A., Wallenstein, T., Lajoie, G., Wolf, G., Krishnaswamy, S.*, \& Turk-Browne, N.B.* (2023). Multi-view manifold learning of human brain-state trajectories. \textit{Nature Computational Science}. 3(3), 240-253,\\ doi:10.1038/s43588-023-00419-0\\
    \small{$\bullet$ Analysis repository: github.com/ericabusch/tphate\_analysis\_capsule}\\
    \small{$\bullet$ PIP package: pypi.org/project/TPHATE/}\vspace{0.2cm}}

\noindent{\textbf{Busch, E.L.} \& Krishnaswamy, S. (2023). Revealing trajectories of the mind via non-linear manifolds of brain activity. \textit{Nature Computational Science}. 3(3), 192-193, doi.org/10.1038/s43588-023-00423-4 \textit{Invited research briefing}.}\vspace{0.2cm}

\noindent{Huang, J.*, \textbf{Busch, E.L.*}, Wallenstein, T.*, Gerasimiuk, M., Benz, A., Lajoie, G., Wolf, G., Turk-Browne, N.B., \& Krishnaswamy, S. (2022). Learning shared neural manifolds from multi-subject FMRI data. \textit{Proceedings of the 32nd IEEE Machine Learning for Signal Processing}. doi:10.1109/MLSP55214.2022.9943383\vspace{0.2cm}}

\noindent{\textbf{Busch, E.L.*}, Slipski, L.*, Feilong, M., Guntupalli, J., Visconti di Oleggio Castello, M., Huckins, J., Nastase, S., Gobbini, M.I., Wager, T., \& Haxby, J. (2021). Hybrid hyperalignment: A single high-dimensional model of shared information embedded in cortical patterns of response and functional connectivity. \textit{NeuroImage.} 233, doi:10.1016/j.neuroimage.2021.117975\\
    \small{$\bullet$ Analysis and software repository: github.com/ericabusch/hybrid\_hyperalignment\_neuroimage}}

\subsection*{Manuscripts}

\noindent{\textbf{Busch, E.L.,} Fincke, E.C., Lajoie, G., Krishnaswamy, S., \& Turk-Browne, N.B. Accelerated learning of a noninvasive human brain-computer interface via manifold geometry. (Article under review), Preprint doi:10.1101/2025.03.29.646109}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.,} Turk-Browne, N.B., \& Baskin-Sommers, A.R. Revamping neuroimaging analysis to reveal biomarkers of adolescent mental health. (Invited Perspective under review)\vspace{0.2cm}}

\noindent{\textbf{Busch, E.L.,} \& Turk-Browne, N.B. Intrinsic dimensionality of brain activity manifolds across diverse tasks and development. (In prep)\vspace{0.2cm}}

\noindent{\small{*Denotes equal contribution.}}

% --- Section: Invited Talks ---
\section*{Invited talks}
\noindent{Workshop on Functional Alignment}\hfill\textit{Upcoming: Sept. 2025}\\
\noindent{\textit{\small{Center for Cognitive Neuroscience, Dartmouth College}}}\vspace{0.2cm}

\noindent{Center for Neuroscience Imaging Research Seminar\hfill\textit{Upcoming: July 2025}}\\
\noindent{\textit{\small{Sungkyunkwan University, Suwon, South Korea}}}\vspace{0.2cm}

\noindent{{International Symposium on Decoded Neurofeedback}\hfill\textit{Upcoming: July 2025}\\
\noindent{\textit{\small{Advanced Telecommunications Research Institute, Kyoto, Japan}}}\vspace{0.2cm}

\noindent{{Manhattan Area Memory Meeting}\hfill June 2025\\
\noindent{\textit{\small{Columbia University's Zuckerman Institute}}}\vspace{0.2cm}

\noindent{fMRI Brown Bag}\hfill May 2025}\\
\noindent{\textit{\small{Center for Cognitive Neuroscience, Dartmouth College}}}\vspace{0.2cm}

\noindent{CompCog Joint Lab Meeting}\hfill Apr. 2025}\\
\noindent{\textit{\small{Department of Cognitive Science, Yale University}}}\vspace{0.2cm}

\noindent{Schoenbaum and Kahnt Labs Meeting}\hfill Apr. 2025\\
\noindent{\textit{\small{National Institute on Drug Abuse}}}\vspace{0.2cm}

\noindent{Cognitive Science Group Meeting}\hfill Apr. 2025\\
\noindent{\textit{\small{Johns Hopkins University}}}\vspace{0.2cm}

\noindent{Magnetic Resonance Research Center fMRI Lecture Series}\hfill Dec. 2024\\
\noindent{\textit{\small{Department of Radiology, Yale University}}}\vspace{0.2cm}

\noindent{Kavli at Yale 20th Anniversary Symposium}\hfill Sept. 2024\\
\noindent{\textit{\small{Kavli Institute for Neuroscience, Yale University}}}\vspace{0.2cm}

\noindent{ABCD Insights \& Innovations Meeting}\hfill Mar. 2024\\
\noindent{\textit{\small{National Institute of Health}}}\vspace{0.2cm}

\noindent{{BrainWorks Projects in Progress}\hfill Nov. 2023}\\
\noindent{\textit{\small{Wu Tsai Institute at Yale University}}}\vspace{0.2cm} 

\noindent{{Shine Lab Meeting}\hfill Apr. 2023}\\
\noindent{\textit{\small{The University of Sydney}}}\vspace{0.2cm} 

\noindent{{MRI Users Meeting}\hfill Oct. 2022}\\
\noindent{\textit{\small{FAS Brain Imaging Center, Yale University}}}\vspace{0.2cm} 

\noindent{{Imaging Analytics Meeting}  \hfill Sept. 2022\\
\noindent{\textit{\small{Adolescent Brain and Cognitive Development (ABCD) project resting-state fMRI working group}}}\vspace{0.2cm}

\noindent{{Current Works in Behavior, Genetics, and Neuroscience}, Yale University \hfill Apr. 2022}\\
\noindent{\textit{\small{Yale University Department of Psychology}}}\vspace{0.2cm}

\noindent{{FINN Lab Meeting}\hfill Apr. 2021}\\
\noindent{\textit{\small{Department of Psychological and Brain Sciences, Dartmouth College}}}\vspace{0.2cm} 

% --- Section: Posters ---

\section*{Conference presentations}
\noindent{\textbf{Busch, E.L.},  \& Turk-Browne, N.B. (2025) Intrinsic dimensionality of brain activity manifolds across tasks and development. \textit{Poster at 8th Annual Conference on Cognitive Computational Neuroscience.} Amsterdam, Netherlands}\vspace{.2cm}

\noindent{\textbf{Busch, E.L.}, \& Turk-Browne, N.B. (2025) Developmental differences in the intrinsic dimensionality of regional brain activity. \textit{Poster at the Cognitive Neuroscience Society Annual Meeting.} Boston, M.A., USA.}\vspace{.2cm}

\noindent{\textbf{Busch, E.L.}, Fincke, E.C., Lajoie, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2024) Learning along the manifold of human brain activity via real-time neurofeedback. \textit{Oral Presentation at the Real-time Functional Imaging and Neurofeedback (rt-FIN) Meeting.} Heidelberg, Germany.}\vspace{.2cm}

\noindent{\textbf{Busch, E.L.}, Fincke, E.C., Lajoie, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2024) Learning along the manifold of human brain activity via real-time neurofeedback. \textit{Contributed Talk and Poster at 7th Annual Conference on Cognitive Computational Neuroscience.} Cambridge, M.A., USA.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Conley, M.I., \& Baskin-Sommers, A. (2024). Using manifold learning to uncover the embedded brain and implications for mental health in youth. \textit{Poster at the Organization for Human Brain Mapping Annual Meeting.} Seoul, South Korea.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Fincke, E.C., Lajoie, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2024). Learning on the manifold of human brain activity through real-time neurofeedback. \textit{Poster at the Organization for Human Brain Mapping Annual Meeting.} Seoul, South Korea.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Fincke, E.C., Lajoie, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2023). Learning on the manifold of human brain activity through real-time neurofeedback. \textit{Talk at the Society for Neuroscience Annual Meeting Nanosymposium on Neural Decoding and Neuroprosthetics.} Washington, D.C., USA.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Yates, T.S., \& Turk-Browne, N.B. (2023). Tasks constrain the intrinsic dimensionality of activity in non-selective cortex. \textit{Poster at the 7th Annual Conference on Cognitive Computational Neuroscience.}, Oxford, United Kingdom.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.,} Bhaskar, D., Letrou, A., Zhang, X., Noah, J.A., Lajoie, G., Hirsch, J., Turk-Browne, N.B., Krishnaswamy, S. (2022). An encoder-decoder framework for cross-modal translation of brain imaging data. \textit{Poster and selected lightning talk at the Montreal AI-Neuroscience Meeting.} Montreal, QC, Canada.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Letrou, A., Huang, J., Lajoie, G., Wolf, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2022). A neural manifold learning framework for real-time fMRI neurofeedback. \textit{Poster at the Society for Neuroscience Annual Meeting.} San Diego, CA, USA.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Letrou, A., Huang, J., Lajoie, G., Wolf, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2022). A neural manifold learning framework for real-time fMRI neurofeedback. \textit{Poster at the Real-time Functional Imaging and Neurofeedback Meeting.} New Haven, CT, USA.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.,} Rapuano, K.M., Anderson, K.M., Rosenberg, M.D., Watts, R., Casey, BJ, Haxby, J.V., \& Feilong, M. (2022). Heritable template underlies reliable idiosyncrasies in the developing fine-scale connectome. \textit{Poster at the Organization for Human Brain Mapping Annual Meeting.} Glasgow, Scotland.}\vspace{0.2cm}

\noindent{Letrou, A., \textbf{Busch, E.L., }\& Turk-Browne, N.B., (2022). Relating neural dynamics and emotion dynamics with nonlinear manifold learning. \textit{Poster and talk at the Social and Affective Neuroscience Society Annual Meeting.}}\vspace{0.2cm}

\noindent{Roskies, A., Walton, A., Roth, R.M., \textbf{Busch, E.L.,} Holtzheimer, P.E., (2022). Measuring the dimensions of agency: A data-driven approach. \textit{Poster at the Philosophy of Science Association}. Pittsburgh, PA.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Huang, J., Benz, A., Wallenstein, T., Lajoie, G., Wolf, G., Krishnaswamy, S., \& Turk-Browne, N.B. (2021). Manifold learning to capture brain-state trajectories in fMRI. \textit{Poster at the Society for Neuroscience Annual Meeting.}}\vspace{0.2cm}

\noindent{Walton, A.E., Nizzi, M.C., West, B., Mofe, E., Roth, R.M., \textbf{Busch, E.L.,} Holtzheimer, P.E., \& Roskies A.L. (2021). The impact of anxiety and depression on dimensions of agency. \textit{Poster at the 7th Annual NIH BRAIN Initiative Annual Meeting.}}\vspace{0.2cm}

\noindent{Sivitilli, D.M., Weertman, W.L., \textbf{Busch, E.L.}, Ullmann, J.F., Smith, J.R., Gire, D.H. (2021). Strategies of single arm foraging in Octopus rubescens in the absence of visual feedback. \textit{Poster at the Society for Integrative and Comparative Biology.}}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Haskins, A.J., Isik, L., \& Robertson, C.E. (2020) A deep learning approach to understanding real-world scene perception in autism. \textit{Presidential Undergraduate Research Symposium, Dartmouth College.}}\vspace{0.2cm}

\noindent{Walton, A.E., \textbf{Busch, E.L.}, Ratoff, W., Smith, W., Holtzheimer, P.E., \&  Roskies, A.L. (2020). Developing an agency assessment tool for understanding changes in agency with neurointerventions: Preliminary results. \textit{Poster at the 6th Annual NIH BRAIN Initiative Annual Meeting.}}\vspace{0.2cm}

\noindent{Botch, T.L., \textbf{Busch, E.L.}, \& Robertson, C.E. (2020). Application of deep neural networks to model omnidirectional gaze behavior in VR. \textit{Poster at the Vision Sciences Society Annual Meeting.}}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Sivitilli, D.M., \& Gire, D.H. (2019). Using deep learning to model octopus arm motion. \textit{Poster and talk at the Center for Neurotechnology Research Symposium.} Seattle, WA, USA.}\vspace{0.2cm}

\noindent{\textbf{Busch, E.L.}, Ma, F., Nastase, S.A., \& Haxby, J.V. (2019). Individual differences in fine-grained neural correlates of mental states. \textit{Poster at the Wetterhahn Science Symposium.} Hanover, NH, USA.}\vspace{0.2cm}

% --- Section: Teaching experience ---

\section*{Teaching experience}

\noindent{Instructor, Interdepartmental Neurosci. Program, \textit{Yale University} \hfill Aug. 2024 \& 2025\\
\small{fMRI Tutorial, INP First-Year Student Bootcamp.}\vspace{0.2cm}}

\noindent{Guest Lecturer, CPSC 663: Deep Learning, \textit{Yale University }\hfill Apr. 2025\vspace{0.2cm}}

\noindent{Guest Lecturer, PSYC 220: Images of Mind,\textit{ University of Illinois} \hfill Mar. 2025\vspace{0.2cm}}

\noindent{Teaching Fellow, Department of Psychology, \textit{Yale University} \hfill Spring 2022 \& 2023\\
\small{PSYC 258/558/NCSI 258: Computational methods in human neuroscience.}\vspace{0.2cm}}
 
\noindent{Teaching Fellow, Department of Psychology, Yale University \hfill Fall 2022\\
\textit{NSCI 160/PSYC 160: The human brain.}\vspace{0.2cm}}

\noindent{Guest lecturer, NSCI 270: Advanced neuroimaging analysis methods, \textit{Yale University} \hfill Nov. 2021}\vspace{0.2cm}

\noindent{Teaching Fellow, Department of Psychology,\textit{ Yale University} \hfill Fall 2021\\
\small{PSYC 270/NCSI 270: Research methods in cognitive neuroscience.}\vspace{0.2cm}}

\noindent{Teaching Assistant, Department of Computer Science, \textit{Dartmouth College} \hfill Spring 2020\\
\small{COSC 74: Machine learning and statistical data analysis}\vspace{0.2cm}}

\noindent{Teaching Assistant, Department of Psychological \& Brain Sciences, \textit{Dartmouth College} \hfill Winter 2019\\
\small{PSYC 6: Introduction to neuroscience}\vspace{0.2cm}}

\noindent{Peer Tutor, Tutor Clearinghouse, \textit{Dartmouth College} \hfill 2017 - 2020\\
\small{SPAN 1-3 (Intro Spanish), SPAN 9 (Culture and Conversation: Advanced), SPAN 20 (Writing and Reading), COSC 1 (Intro to Programming and Computation), COSC 10 (Object-Oriented Programming), COSC 50 (Software Design), COSC 74 (Machine Learning), PSYC 6 (Intro to Neuroscience), PSYC 10 (Statistics), COGS 1 (Intro to Cognitive Science)}\vspace{0.2cm}}

\noindent{Cryptography Instructor, \textit{Sonia Kovalevsky Math Day at Dartmouth College}\hfill Apr. 2018\vspace{0.2cm}}

\noindent{College Access Coach, \textit{Let's Get Ready} \hfill Summer 2017 \\
\small{Taught SAT and college application preparatory courses for high school students from historically underrepresented backgrounds in New York Public Schools.}\vspace{0.2cm}}

\noindent{Instructor, \textit{Center for Gifted Youth, Long Island University}\hfill Summer 2017\\
\small{Designed and taught courses on mathematics and genetics for advanced middle school students.}\vspace{0.2cm}}

\noindent{Private tutor \hfill 2012--2024\\
\small{K-12: NY State Regents math and sciences, English, History, Spanish; AP: Calculus AB and BC, Statistics, Physics, Computer Science; SAT / ACT; UG: Algebra, Graph Theory, Spanish.}\vspace{0.2cm}}

% --- Section: Service and outreach ---

\section*{Service and outreach}
\noindent{Trainee Committee, Cognitive Computational Neuroscience Society}\hfill2024\vspace{0.2cm}\\
\noindent{Organizer \& Founding Member, Innovators in Cognitive Neuroscience Seminar Series\hfill 2020--Present}\vspace{0.2cm}\\
\noindent{Fellow \& Founding Member, Wu Tsai Institute Student, Postbac, \& Postdoc Collective}\hfill 2022--Present\vspace{0.2cm}\\
\noindent{Yale Psychology Colloquium Committee} \hfill 2021--2023\vspace{0.2cm}\\
\noindent{Sneak Peek Mentor, Yale Psychology Diversity Committee} \hfill 2021--2023\vspace{0.2cm}\\
\noindent{Facilitator and mentor, Dartmouth Leadership, Attitudes, and Behaviors Program\hfill 2018--2020\\
\noindent{\textit{\small{Ran 10-week workshops on value-driven leadership through the Nelson A. Rockefeller Center for Public Policy}}}\vspace{0.2cm}\\
\noindent{SIBS Mentorship Program Director, Dartmouth Center for Social Impact}\hfill 2016--2020 \\
\noindent{\textit{\small{Mentored for and directed a one-on-one mentorship program for Dartmouth undergrads and local youth involved in county social services. Coordinated with mentors, teachers, parents, and social workers; responsible for training mentors.}}}\vspace{0.2cm}

\subsection*{Mentorship}
\noindent{Dominic Gearing (Yale undergraduate)\hfill 2024--Present\\
David Lee (Yale undergraduate)\hfill 2024--Present\\
E. Chandra Fincke (Yale undergraduate and honors thesis student)\hfill 2022--2024\\
\textit{Now: Space Operations Officer, United States Space Force}\\
Ariadne Letrou (Lab manager and postgraduate researcher)\hfill 2021--2023\\
\textit{Now: PhD student, Princeton Psychology (PI: Ken Norman)}\\
Kyle Andruczk (Yale undergraduate)\hfill 2022--2023\\
\textit{Now: Full stack software engineer}}

\subsection*{Ad-hoc reviewing}
Nature Methods, Nature Human Behavior, Nature Computational Science, Journal of Neuroscience, Proceedings of the National Academy of Sciences (PNAS), Imaging Neuroscience, International Conference on Learning Representations (ICLR), Neural Information Processing Systems (NeurIPS), Cognitive Computational Neuroscience (CCN).

\subsection*{Other skills}
\textit{Neuroimaging}: rt-cloud (Real-time fMRI with cloud computing), MRI operator certified, MEG/EEG experienced. BrainIAK \& PyMVPA Contributor, FSL, FreeSurfer, AFNI, Reproducible Neuroimaging.\vspace{0.2cm}\\
\textit{Programming}: Python, BASH, C, C++, C\# for Unity, Java, MATLAB, R, HTML, Unity, PsychoPy, PsychToolbox, PyTorch, Keras, TensorFlow.\vspace{0.2cm}\\
\textit{Languages}: Spanish (fluent), Italian and Portuguese (intermediate).\vspace{0.2cm}\\ 
\textit{Miscellaneous}: Competitive equestrian, pet enthusiast, runner, illustrator, freelance data scientist.\\
\end{document}
